
The following publications have arisen from this PhD work. Where copyright is retained by the publisher, text and figures are reprinted with permission, as detailed in Appendix \ref{app:5-copyright}.

\vspace{\frontmatterbaselineskip}

\textbf{Theory and simulation of hybrid halide perovskites } 

Text and figures 1--4 adapted from
\href{https://doi.org/10.1063/1.4984964}{Whalley, L. D., Frost, J. M., Jung, Y. -K. and Walsh, A. (2017). Perspective: Theory and simulation of hybrid halide perovskites. \textit{The Journal of Chemical Physics}, 146(22), p.220901.} © 2017 CC-BY
\vspace{\frontmatterbaselineskip}

\textbf{Electronic band non-parabolicity}

Text and figures 1--11 adapted from
\href{https://doi.org/10.1103/PhysRevB.99.085207}{Whalley, L. D., Frost, J., Morgan, B. and Walsh, A. (2019). Impact of nonparabolic electronic band structure on the optical and transport properties of photovoltaic materials. \textit{Physical Review B}, 99(8).} © 2019 American Physical Society
\vspace{\frontmatterbaselineskip}

\textbf{Electron-phonon and phonon-phonon coupling}

Excerpts and figures 2--4 adapted from
\href{https://doi.org/10.1103/PhysRevB.94.220301}{Whalley, L. D., Skelton, J. M., Frost, J. M. and Walsh, A. (2016). Phonon anharmonicity, lifetimes, and thermal transport in \ce{CH3NH3PbI3} from many-body perturbation theory. \textit{Physical Review B}, 94(22).} © 2016 American Physical Society

Excerpts and figures 1,5--6 adapted from
\href{https://doi.org/10.1021/acsenergylett.7b00862}{Frost, J. M., Whalley, L. D and Walsh, A. (2017). Slow Cooling of Hot Polarons in Halide Perovskite Solar Cells. \textit{ACS Energy Letters}, 2(12), pp.2647-2652.} © 2017 CC-BY
\vspace{\frontmatterbaselineskip}

\textbf{Electron trapping at H-centre defects}

Excerpts adapted from
\href{https://doi.org/10.1021/acsenergylett.7b00995}{Whalley, L. D., Crespo-Otero, R. and Walsh, A. (2017). H-Center and V-Center Defects in Hybrid Halide Perovskites. \textit{ACS Energy Letters}, 2(12), pp.2713-2714.} © 2017 American Chemical Society 
\vspace{\frontmatterbaselineskip}

\textbf{Appendix C: effmass: An effective mass package}

Text reprinted from
\href{https://doi.org/10.21105/joss.00797}{Whalley, L. D. (2018). effmass: An effective mass package. \textit{Journal of Open Source Software}, 3(28), p.797.} © 2018 CC-BY 


